A cautionary note on the use of Ornstein Uhlenbeck models in macroevolutionary studies

### 2015-08-03 Manuscript/ohyou.tex
Update email address

  $^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
  $^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
  $^3$ Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK.\\
  $^4$ Department of Animal and Plant Sciences, University of Sheffield, Sheffield S10 2TN, UK.\\
  $^5$ School of Biological Sciences, University of Reading, Reading, Berkshire, RG6 6BX, UK.\\
  $^*$ Corresponding author: nhcooper12@gmail.com, Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK.\\ Tel: +44 20 7942 5000.\\
  $^\dag$These authors contributed equally.
}}

>>>>

  $^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
  $^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
  $^3$ Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK.\\
  $^4$ Department of Animal and Plant Sciences, University of Sheffield, Sheffield S10 2TN, UK.\\
  $^5$ School of Biological Sciences, University of Reading, Reading, Berkshire, RG6 6BX, UK.\\
  $^*$ Corresponding author: natalie.cooper@nhm.ac.uk, Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK.\\ Tel: +44 20 7942 5000.\\
  $^\dag$These authors contributed equally.
}}
